### 2021-11-06 manuscript.Rmd
typographic changes to text+figures

Because the use of group-sequential procedures allows for early stopping, it generally reduces the average sample size needed (with certain exceptions; e.g., when the true effect size is equal to or close to zero, the use of sequential procedures tends to increase the average sample size needed). For example, if a researcher wants to conduct a one-sided, two-sample *t* test ($H_0:~\delta$ = 0 against $H_+:~\delta > 0$) with 80% power to detect a Cohen's *d* (i.e., a standardized mean difference) of 0.5, a conventional Null Hypothesis Significance Test with an overall $\alpha$ of 5% would require `r n_fixed` participants per group. Using the Pocock-like GS design outlined above, the same study can be conducted with only `r n_p` participants per group per look. Using the O'Brien-Fleming like design outlined above, this same study can be conducted with `r n_of[1]` participants per group during the first look, and `r n_of[2]` participants per group during the last two looks. Below, I briefly outline the decision-theoretic procedure of GS designs.

@@

The SBF procedure has several properties of interest. First, it is symmetric: it allows researchers to examine whether the obtained data is better predicted by, for example, $H_+$ than $H_0$, or vice versa. Second, it is highly flexible: it allows researchers to take as many looks at incoming data as desired [even after every study participant\; @schonbrodt2017]. Third, it does not allow type I and type II error rates to be defined a priori [although simulations can be run to choose an optimal design that controls expected error rates, @schonbrodt2018; @schonbrodt2017; @stefan2020]. Fourth, it allows (and requires) researchers to express their uncertainty about the expected effect size by means of a prior distribution.

Again, we consider the example of a researcher running a one-sided, two-sample *t* test between $H_0:~\delta$ = 0 and $H_+:~\delta > 0$. To follow the SBF procedure, the researcher needs to prespecify two things: (a) the prior distribution for the standardized effect size $\delta$ under $H_+$ and (b) the decision threshold _t_* for the Bayes Factor. Excellent guidance on these important decisions can be found in @schonbrodt2017. Ideally, a Bayes Factor Design Analysis or simulations can be run to choose an optimal design that controls expected error rates [@schonbrodt2018].

To reflect the expectation of a "medium" effect size, a researcher can, for example, choose the default prior distribution [i.e., a Cauchy distribution with scale parameter *r* = $\sqrt2/2$\; @morey2011; @schnuerch2020; @schonbrodt2017]. Alternatively, a researcher can rely on an informed prior distribution that incorporates prior knowledge about the effect size, gathered from expert knowledge, previous work, or theoretical considerations [@stefan2020]. In addition, the researcher could (for example, on the basis of simulations) choose $BF_{+0}$ = 3 as a decision threshold [commonly referred to as "*moderate evidence*"\; @schonbrodt2017]. This decision threshold _t_* implies that the researcher is content to stop sampling once the data is 3 times more likely under $H_+$ than under $H_0$, or vice versa. Figure 2A (2B) provides a visual example of a situation in which the Bayes Factor indicates that the data is 3 times more likely under $H_+$ ($H_0$).

The Sequential Bayes Factor and the Group-Sequential Procedures address different questions, each interesting in their own right. Group-sequential procedures (as well as the traditional Null Hypothesis Significance Test and the Independent Segments Procedure described below) raise the question "*On the basis of a decision rule under which the long-run probability of rejecting a true null hypothesis will be no more than $\alpha$%, can the null hypothesis be rejected?*" The Sequential Bayes Factor procedure, on the other hand, considers "*On the basis of a prespecified threshold and desired error rates under the assumption of a specific $H_0$ and $H_+$, can we conclude that there is sufficient evidence for $H_0$ or $H_+$?*"

@@

  *
1. Randomly sample $N_{\text{Bayes}}$ observations from the specified population(s) 
2. Run the test(s) of interest (e.g., a one-sided default Bayes Factor two-sample *t* test)
  a. if $BF_{+0} \ge t*$: decide to reject $H_0$ (support $H_+$) and end the experiment
  b. if $BF_{+0} \le 1/t*$: decide to reject $H_+$ (support $H_0$) and end the experiment
  c. if $1/t*~< BF_{+0} < t*$: collect additional observations and repeat step 2 on the cumulative data
3. Continue until the Bayes Factor crosses one of the thresholds, or until the maximum *N* has been reached

@@

  a. if $p \le \alpha_{strong}$: decide to reject $H_0$ and end the experiment 
  b. if $p > \alpha_{weak}$: decide not to reject $H_0$ and end the experiment
  c. if $\alpha_{strong} < p \le \alpha_{weak}$: discard the data, collect a new batch of $N_{\text{ISP}} observations, and repeat step 2 on this independent batch of data

@@

1. For the fixed sample hypothesis test paired with an equivalence test, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{1,k}$)
3. For the SBF procedure, $\delta$ > 0 and the decision was made to reject the null hypothesis ($BF_{+0}~\ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{strong}$ in segments 1:$k_{max}-1$ or *p* $\le \alpha_{weak}$ in the final segment $k_{max}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{1,k}$)
3. For the SBF procedure, $\delta$ = 0 and the decision was made to reject the null hypothesis ($BF_{+0} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{strong}$ in segments 1:$k_{max}-1$ or *p* $\le \alpha_{weak}$ in the final segment $k_{max}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta$ = 0 and the decision was made to conclude statistical equivalence [*p* $\le \alpha$ for both *p*-values of a Two One-Sided Tests [TOST] procedure\; @lakens2018]
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ = 0 and the decision was made to stop for futility (*p* $\ge \alpha_{0,k}$)
3. For the SBF procedure, $\delta$ = 0 and the decision was made to support the null hypothesis ($BF_{0+} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ = 0 and the decision was made to stop in an early segment (*p* $> \alpha_{weak}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta > 0$ and the decision was made to conclude statistical equivalence ($p_{\text{TOST}, 1:2}$ $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ > 0 and the decision was made to stop for futility (*p* $\ge \alpha_{0,k}$)
3. For the SBF procedure, $\delta$ > 0 and the decision was made to support the null hypothesis ($BF_{0+} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ > 0 and the decision was made to stop in an early segment (*p* $> \alpha_{weak}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, the procedure failed to reject the null hypothesis or conclude statistical equivalence ($p_{\text{fixed}} > \alpha$ and $p_{\text{TOST},1:2} > \alpha$ )
2. For the Pocock and O'Brien-Fleming procedures, $k_{max}$ was reached and ended in a failure to reject the null hypothesis ($p > \ \alpha_1$)
3. For the SBF procedure, $k_{max}$ was reached and neither of the thresholds was met ($1/t*~< BF_{+0} < t*$)
4. For the Independent Segments Procedure, $k_{max}$ was reached and ended in a failure to reject the null hypothesis (*p* > $\alpha_{weak}$)

@@

The parameters for the Sequential Bayes Factor procedure were chosen to allow for maximum comparability with the frequentist sequential procedures, which correspond to a one-tailed hypothesis test powered to detect a hypothesized population effect size of $\delta$ = 0.5 with $\alpha$ = .05 and $k_{max} = 3$ looks. To calculate the Bayes Factor, I used an informed prior (a normal distribution centered at the hypothesized effect size, $\delta = 0.5$). To incorporate information about the sidedness of the hypothesized effect, the prior distribution was truncated at $\delta = 0$ to include only positive values. Thus, like in the one-sided *t*-tests described above, we compare $H_0:~\delta = 0$ to $H_+:~\delta > 0$.

For the SBF procedure, I ran simulations to choose an optimal sample size (paired to the other procedures under study, with $k_{max}$ = 3 equally spaced looks) and Bayes Factor threshold, such that the overall error rate would approach that of the frequentist procedures (i.e., a false negative rate of 20% and a false positive rate of 5%). In the main paper, I report the results of a max-SBF procedure with the Bayes Factor threshold set to 3 for $H_+$ and 1/3 for $H_0$, the sample size set to $N_{\text{Bayes}}$ = 25 per group per look with $k_{max}$ = 3 looks, and a normal prior distribution centered at $\delta = 0.5$ with $\sigma^2 = 0.3$. In the supplemental materials at [link], results can be found for simulations that vary additional parameters for the max-SBF procedure. Of note, as discussed above, the Sequential Bayes Factor can be implemented much more flexibly (i.e., with as many looks as desired, without a maximum sample size). However, to make the sequential procedures as comparable as possible and to account for practical considerations that researchers may have, each procedure is each implemented with $k_{max}$ = 3 looks.

@@

## *Sequential-Bayes Factor*
1. Randomly sample $N_{\text{Bayes}}$ observations from each of the two specified populations
2. Run a one-sided, two-sample Bayes Factor *t* test on the mean difference between the two samples
  a. if $BF_{+0} \ge 3$: decide to reject $H_0$ (support $H_1$) and end the experiment
  b. if $BF_{+0} \le 1/3$: decide to reject $H_1$ (support $H_0$) and end the experiment
  c. if $1/3 < BF_{10} < 3$: collect $N_{\text{Bayes}}$ additional observations and repeat step 2 on the cumulative data
3. Continue until the Bayes Factor crosses one of the thresholds, or until the maximum *N* ($N_{\text{Bayes}} * k_{max}$) has been reached
4. To estimate the uncorrected standardized effect size, calculate Cohen's *d*
5. To estimate the bias-adjusted standardized effect size, calculate the mean of the posterior distribution using a two-sided model [@vandoorn2020]
6. Repeat 10,000 times

@@

The error rates involved in the procedures under discussion are shown in Table 2A, Table 2B, and Figure 4. Table 2A describes the rates of True Negative, Inconclusive, and False Positive results when the true population effect size $\delta$ = 0; Table 2B describes the rates of True Positive, Inconclusive, and False Negative results when the true population effect size $\delta$ = 0.50. As can be read from the tables, the frequentist procedures all perform as expected: 4-5% of simulations rejected the null hypothesis when $\delta$ = 0 (i.e., a type I error rate of 4-5%; see the False Positive column Table 2A) and 80-81% of simulations rejected the null hypothesis when $\delta$ = 0.5 (i.e., a type II error rate of 19-20%; see the True Positive column of Table 2B).

In addition, the results speak to the ability of using simulations to design an efficient Bayesian hypothesis testing procedure with attractive long-run properties. In this case, the False Positive rate of the SBF procedure is 4% and the True Positive rate of the SBF procedure is 78%. In addition, when a true population effect size exists, the SBF procedure consistently leads to a lower False Negative rate (and a higher rate of Inconclusive results) than its frequentist counterparts. This is in part due to the high(er) bar that the Bayes Factor requires to support the Null Hypothesis. In this case, the alternative hypothesis ($H_+:~\delta > 0$) has a within-model prior centered on zero (i.e., a Cauchy distribution with scale parameter *r* = $\sqrt2/2$). For this model to be dominated by the null hypothesis ($H_0:~\delta = 0$) when in fact a true population effect exists, it takes a large number of misleading samples in which the effect size is close to zero. Thus, a Bayesian will have a harder time concluding evidence in favor of the null (a False Negative) when a population effect exists.

In line with previous findings [@schonbrodt2017; @schonbrodt2018; @stefan2020], I find that simulation-based approaches allow researchers to choose an optimal Sequential Bayes Factor design that controls expected error rates. It has previously been shown that the maximum-flexibility SBF procedure -- with appropriate choices for the decision threshold and the prior distribution of effect sizes under the alternative hypothesis -- can perform (at least) as well as other (sequential) procedures in terms of false-positive and false-negative error rates [@schonbrodt2017; @stefan2020]. Here, I show that this observation holds when we use a restricted version of the SBF with $k_{max}$ = 3 equally spaced looks.

@@

Table 3 and Figure 5 show the average sample size required for the procedures under investigation, as a function of the true population effect size. As discussed, the fixed-sample procedure requires 51 participants per group. As can be read from Table 3 and Figure 5, the sequential procedures allow for a reduction in the average sample size required. Across the procedures, efficiency gains appear to be rather similar. When the true population effect size is relatively large, the O'Brien-Fleming approach is slightly less efficient than its counterparts. This can be explained by the relatively stringent $\alpha_1$ levels of the O'Brien-Fleming procedure in earlier segments (recall that, for the O'Brien-Fleming-like procedure, $\alpha_{1,1}$ = `r alpha_of[1]` and $\alpha_{1,2}$ = `r alpha_of[2]`).

@@

Figure 6 shows the empirical distribution of effect size estimates stemming from the five hypothesis testing procedures when the true effect size $\delta$ = 0.5. Effect size estimates stemming from the fixed sample hypothesis test are, as expected, normally distributed around the true effect size ($\delta$ = 0.5). As we can see, the distribution of effect size estimates stemming from the sequential procedures have a somewhat odd shape. This is to be expected [see, for example, @goodman2007]. The distribution of observed effects is more spread out for the sequential procedures because the experiments that stopped early have smaller sample sizes and higher variability in effect size estimates. In addition, we observe left-tailed peaks in the distribution of observed effect sizes. This is a consequence of those experiments that stopped early with a decision to support the null (i.e., False Negative results).

For the SBF, the median effect size estimate (*d* = 0.51) is very close to the true value ($\delta$ = 0.5). The GS procedures each have a slight bias in the median effect size estimate: *d* = 0.54 for the O'Brien-Fleming-like procedure and *d* = 0.57 for the Pocock-like procedure. The bias in the median effect size estimate of the ISP, however, is severe (*d* = 0.66; an exaggeration ratio of 1.33). The distribution of effect size estimates stemming from the ISP is bi-modal.

@@

In the supplemental files, readers can find that this observation is not merely idiosyncratic to the test chosen (a two-sample *t* test with $\alpha$ = .05 and $\beta = .20$ for a hypothesized population effect size $\delta$ = 0.5). In contrast, across dozens of different test specifications, effect size estimates stemming from the ISP are consistently bi-modal and systematically exclude the true population effect size from being observed.

@@

<!-- Add in discussion/limitation section: We do not discuss adaptive designs, which extend GS designs and allow for even more flexibility while controlling error rates.  -->
<!-- Discuss the power of the individual segments. Practical advice (can lead to guidance on choosing alpha strong; make sure that the alpha strong you set does not exclude the effect size you are interested in. Write reveal.effectsize function): You have to make sure that the individual segments are each powered to at least 50 percent to detect the hypothesized effect size: otherwise, the critical effect size will be higher than the hypothesized effect size, and you will thus systematically discard the effect sizes that you intended to detect! Show that with the example used, the first two independent segments are powered to ~30%. In all but the last segment, the critical effect size (the effect size you need to observe to claim significance) is a factor larger than the actual population effect that you powered your test for. It is thus impossible to get an unbiased estimate out of anything but the last segment.  When you obtain an effect size close to the true effect, the ISP procedure forces you to continue to the last segment, and *throw out that data*. (You can even graph this exaggeration ratio: create a table that shows the exact critical effect size for all possible combinations, and then you can just read off that plot that you're setting yourself up for overestimation). -->
<!-- Discuss conditional bias (bias in effect size estimates conditional on stopping early) and unconditional bias (bias in effect size estimates across all studies). All other procedures have low unconditional bias, when you take the late termination studies into account, because they do cumulative analyses — the late termination studies are able to compensate for the bias in the early stage terminations. However, because the independent segments procedure is independent, each individual segment is biased and this is never accounted or compensated for. Thus, the ISP is unique among sequential procedures in that it not only has strong conditional bias (like most sequential procedures): it also has strong unconditional bias. [In this paper, I focused on two properties: conditional bias (bias in effect size estimates conditional on stopping early) and unconditional bias (bias in effect size estimates across all studies). I show that the independent segments procedure is unique among sequential procedures in that it not only has strong conditional bias (like all sequential procedures); it also has strong unconditional bias.] Emphasize that this is also what we see in Figure 3B: we only reject when d > 0.57. (This is not the case for, e.g., Pocock)   -->
<!-- In the language of decision theory, the ISP is inadmissible: its total squared error risk exceeds that of other hypothesis testing procedures no matter what the true effect size may be.  -->
<!-- Change writing on Bayes True Negative. Because I switched to an oracle prior setup, true negative rates actually look great -->
<!-- Also refer to MSE as reducible error  -->
<!-- Maybe add the figure of bimodality for all ISP parameters? Look through previous commits for this. -->
<!-- Emphasize that there is no bias correction available for the ISP, while there is for the SBF and GS. Also emphasize that the ISP is the only procedure that is *not* median unbiased. Check if Lakens' comment makes this point? -->
<!-- Incorporate points from three new Psych Methods papers (Lakens, Sneurch/Erdfelder, Ulrich/Miller) -->
<!-- (To make the point that the setup of the simulations is more practical and realistic than previous ones), Show some data on what scientists actually do, e.g., how often they look at their data when they use the Sequential Bayes Factor. Here's some examples on how SBFs are used in practice https://github.com/nicebread/BFDA/blob/master/BFDA_examples.md  -->

@@

```{r include = F}
E_n = df %>% 
  group_by(name, d_actual) %>% 
  summarize(E_n = mean(n_cumulative)) %>% 
  rename(Procedure = name)

t3 = E_n %>% mutate(E_n = E_n %>% round()) %>% 
  pivot_wider(names_from = d_actual, names_prefix = "*d* = ", values_from = E_n) 
```

```{r, echo = FALSE}
knitr::kable(t3)
```

>>>>

Because the use of group-sequential procedures allows for early stopping, it generally reduces the average sample size needed (with certain exceptions; e.g., when the true effect size is equal to or close to zero, the use of sequential procedures tends to increase the average sample size needed). For example, if a researcher wants to conduct a one-sided, two-sample *t* test ($H_0:~\delta$ = 0 against $H_1:~\delta > 0$) with 80% power to detect a Cohen's *d* (i.e., a standardized mean difference) of 0.5, a conventional Null Hypothesis Significance Test with an overall $\alpha$ of 5% would require `r n_fixed` participants per group. Using the Pocock-like GS design outlined above, the same study can be conducted with only `r n_p` participants per group per look. Using the O'Brien-Fleming like design outlined above, this same study can be conducted with `r n_of[1]` participants per group during the first look, and `r n_of[2]` participants per group during the last two looks. Below, I briefly outline the decision-theoretic procedure of GS designs.

@@

The SBF procedure has several properties of interest. First, it is symmetric: it allows researchers to examine whether the obtained data is better predicted by, for example, $H_1$ than $H_0$, or vice versa. Second, it is highly flexible: it allows researchers to take as many looks at incoming data as desired [even after every study participant\; @schonbrodt2017]. Third, it does not allow type I and type II error rates to be defined a priori [although simulations can be run to choose an optimal design that controls expected error rates, @schonbrodt2018; @schonbrodt2017; @stefan2020]. Fourth, it allows (and requires) researchers to express their uncertainty about the expected effect size by means of a prior distribution.

Again, we consider the example of a researcher running a one-sided, two-sample *t* test between $H_0:~\delta$ = 0 and $H_1:~\delta > 0$. To follow the SBF procedure, the researcher needs to prespecify two things: (a) the prior distribution for the standardized effect size $\delta$ under $H_1$ and (b) the decision threshold _t_* for the Bayes Factor. Excellent guidance on these important decisions can be found in @schonbrodt2017. Ideally, a Bayes Factor Design Analysis or simulations can be run to choose an optimal design that controls expected error rates [@schonbrodt2018].

To reflect the expectation of a "medium" effect size, a researcher can, for example, choose the default prior distribution [i.e., a Cauchy distribution with scale parameter *r* = $\sqrt2/2$\; @morey2011; @schnuerch2020; @schonbrodt2017]. Alternatively, a researcher can rely on an informed prior distribution that incorporates prior knowledge about the effect size, gathered from expert knowledge, previous work, or theoretical considerations [@stefan2020]. In addition, the researcher could (for example, on the basis of simulations) choose $BF_{10}$ = 3 as a decision threshold [commonly referred to as "*moderate evidence*"\; @schonbrodt2017]. This decision threshold _t_* implies that the researcher is content to stop sampling once the data is 3 times more likely under $H_1$ than under $H_0$, or vice versa. Figure 2A (2B) provides a visual example of a situation in which the Bayes Factor indicates that the data is 3 times more likely under $H_1$ ($H_0$).

The Sequential Bayes Factor and the Group-Sequential Procedures address different questions, each interesting in their own right. Group-sequential procedures (as well as the traditional Null Hypothesis Significance Test and the Independent Segments Procedure described below) raise the question "*On the basis of a decision rule under which the long-run probability of rejecting a true null hypothesis will be no more than $\alpha$%, can the null hypothesis be rejected?*" The Sequential Bayes Factor procedure, on the other hand, considers "*On the basis of a prespecified threshold and desired error rates under the assumption of a specific $H_0$ and $H_1$, can we conclude that there is sufficient evidence for $H_0$ or $H_1$?*"

@@

  *
1. Randomly sample $N_{\text{Bayes}}$ observations from the specified population(s) 
2. Run the test(s) of interest (e.g., a one-sided default Bayes Factor two-sample *t* test)
  a. if $BF_{10} \ge t*$: decide to reject $H_0$ (support $H_1$) and end the experiment
  b. if $BF_{10} \le 1/t*$: decide to reject $H_1$ (support $H_0$) and end the experiment
  c. if $1/t*~< BF_{10} < t*$: collect additional observations and repeat step 2 on the cumulative data
3. Continue until the Bayes Factor crosses one of the thresholds, or until the maximum *N* has been reached

@@

  a. if $p \le \alpha_{strong}$: decide to reject $H_0$ and end the experiment 
  b. if $p > \alpha_{weak}$: decide not to reject $H_0$ and end the experiment
  c. if $\alpha_{strong} < p \le \alpha_{weak}$: discard the data, collect a new batch of $N_{\text{ISP}}$ observations, and repeat step 2 on this independent batch of data

@@

1. For the fixed sample hypothesis test paired with an equivalence test, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{1,k}$)
3. For the SBF procedure, $\delta$ > 0 and the decision was made to reject the null hypothesis ($BF_{10}~\ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ > 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{strong}$ in segments 1:$k_{max}-1$ or *p* $\le \alpha_{weak}$ in the final segment $k_{max}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{1,k}$)
3. For the SBF procedure, $\delta$ = 0 and the decision was made to reject the null hypothesis ($BF_{10} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ = 0 and the decision was made to reject the null hypothesis (*p* $\le \alpha_{strong}$ in segments 1:$k_{max}-1$ or *p* $\le \alpha_{weak}$ in the final segment $k_{max}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta$ = 0 and the decision was made to conclude statistical equivalence [*p* $\le \alpha$ for both *p*-values of a Two One-Sided Tests [TOST] procedure\; @lakens2018]
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ = 0 and the decision was made to stop for futility (*p* $\ge \alpha_{0,k}$)
3. For the SBF procedure, $\delta$ = 0 and the decision was made to support the null hypothesis ($BF_{01} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ = 0 and the decision was made to stop in an early segment (*p* $> \alpha_{weak}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, $\delta > 0$ and the decision was made to conclude statistical equivalence ($p_{\text{TOST}, 1:2}$ $\le \alpha$)
2. For the Pocock and O'Brien-Fleming procedures, $\delta$ > 0 and the decision was made to stop for futility (*p* $\ge \alpha_{0,k}$)
3. For the SBF procedure, $\delta$ > 0 and the decision was made to support the null hypothesis ($BF_{01} \ge$ _t_*)
4. For the Independent Segments Procedure, $\delta$ > 0 and the decision was made to stop in an early segment (*p* $> \alpha_{weak}$)

@@

1. For the fixed-sample hypothesis test paired with an equivalence test, the procedure failed to reject the null hypothesis or conclude statistical equivalence ($p_{\text{fixed}} > \alpha$ and $p_{\text{TOST},1:2} > \alpha$ )
2. For the Pocock and O'Brien-Fleming procedures, $k_{max}$ was reached and ended in a failure to reject the null hypothesis ($p > \ \alpha_1$)
3. For the SBF procedure, $k_{max}$ was reached and neither of the thresholds was met ($1/t*~< BF_{10} < t*$)
4. For the Independent Segments Procedure, $k_{max}$ was reached and ended in a failure to reject the null hypothesis (*p* > $\alpha_{weak}$)

@@

The parameters for the Sequential Bayes Factor procedure were chosen to allow for maximum comparability with the frequentist sequential procedures, which correspond to a one-tailed hypothesis test powered to detect a hypothesized population effect size of $\delta$ = 0.5 with $\alpha$ = .05 and $k_{max} = 3$ looks. To calculate the Bayes Factor, I used an informed prior (a normal distribution centered at the hypothesized effect size, $\delta = 0.5$). To incorporate information about the sidedness of the hypothesized effect, the prior distribution was truncated at $\delta = 0$ to include only positive values. Thus, like in the one-sided *t*-tests described above, we compare $H_0:~\delta = 0$ to $H_1:~\delta > 0$.

For the SBF procedure, I ran simulations to choose an optimal sample size (paired to the other procedures under study, with $k_{max}$ = 3 equally spaced looks) and Bayes Factor threshold, such that the overall error rate would approach that of the frequentist procedures (i.e., a false negative rate of 20% and a false positive rate of 5%). In the main paper, I report the results of a max-SBF procedure with the Bayes Factor threshold set to 3 for $H_1$ and 1/3 for $H_0$, the sample size set to $N_{\text{Bayes}}$ = 25 per group per look with $k_{max}$ = 3 looks, and a normal prior distribution centered at $\delta = 0.5$ with $\sigma^2 = 0.3$. In the supplemental materials at [link], results can be found for simulations that vary additional parameters for the max-SBF procedure. Of note, as discussed above, the Sequential Bayes Factor can be implemented much more flexibly (i.e., with as many looks as desired, without a maximum sample size). However, to make the sequential procedures as comparable as possible and to account for practical considerations that researchers may have, each procedure is each implemented with $k_{max}$ = 3 looks.

@@

## *Sequential-Bayes Factor*
1. Randomly sample $N_{\text{Bayes}}$ observations from each of the two specified populations
2. Run a one-sided, two-sample Bayes Factor *t* test on the mean difference between the two samples
  a. if $BF_{10} \ge 3$: decide to reject $H_0$ (support $H_1$) and end the experiment
  b. if $BF_{10} \le 1/3$: decide to reject $H_1$ (support $H_0$) and end the experiment
  c. if $1/3 < BF_{10} < 3$: collect $N_{\text{Bayes}}$ additional observations and repeat step 2 on the cumulative data
3. Continue until the Bayes Factor crosses one of the thresholds, or until the maximum *N* ($N_{\text{Bayes}} * k_{max}$) has been reached
4. To estimate the uncorrected standardized effect size, calculate Cohen's *d*
5. To estimate the bias-adjusted standardized effect size, calculate the mean of the posterior distribution using a two-sided model [@vandoorn2020]
6. Repeat 10,000 times

@@

The error rates involved in the procedures under discussion are shown in Table 2A, Table 2B, and Figure 4. Table 2A describes the rates of True Negative, Inconclusive, and False Positive results when the true population effect size $\delta$ = 0; Table 2B describes the rates of True Positive, Inconclusive, and False Negative results when the true population effect size $\delta$ = 0.50. As can be read from the tables, the frequentist procedures all perform as expected: 5% of simulations rejected the null hypothesis when $\delta$ = 0 (i.e., a type I error rate of 5%; see the False Positive column Table 2A) and 80-82% of simulations rejected the null hypothesis when $\delta$ = 0.5 (i.e., a type II error rate of 18-20%; see the True Positive column of Table 2B).

In addition, the results speak to the ability of using simulations to design an efficient Bayesian hypothesis testing procedure with attractive long-run properties. In this case, the False Positive rate of the SBF procedure is 6% and the True Positive rate of the SBF procedure is 84%. In line with previous findings [@schonbrodt2017; @schonbrodt2018; @stefan2020], I find that simulation-based approaches allow researchers to choose an optimal Sequential Bayes Factor design that controls expected error rates. It has previously been shown that the maximum-flexibility SBF procedure -- with appropriate choices for the decision threshold and the prior distribution of effect sizes under the alternative hypothesis -- can perform (at least) as well as other (sequential) procedures in terms of false-positive and false-negative error rates [@schonbrodt2017; @stefan2020]. Here, I show that this observation holds when we use a restricted version of the SBF with $k_{max}$ = 3 equally spaced looks.

@@

Table 3 and Figure 5 show the average sample size required for the procedures under investigation, as a function of the true population effect size. As discussed, the fixed-sample procedure requires 51 participants per group. As can be read from Table 3 and Figure 5, the sequential procedures allow for a reduction in the average sample size required. Across the procedures, efficiency gains appear to be rather similar. When the true population effect size is relatively small, the max-SBF procedure is less efficient than its frequentist counterparts. When the true population effect size is relatively large, the O'Brien-Fleming approach is slightly less efficient than its counterparts. This can be explained by the relatively stringent $\alpha_1$ levels of the O'Brien-Fleming procedure in earlier segments (recall that, for the O'Brien-Fleming-like procedure, $\alpha_{1,1}$ = `r alpha_of[1]` and $\alpha_{1,2}$ = `r alpha_of[2]`). Across all true effect sizes, the Pocock-like procedure, with our chosen parameters, provides the greatest efficiency gains.

@@

Figure 6 shows the empirical distribution of effect size estimates, along with the available bias-adjusted estimates, stemming from the five hypothesis testing procedures when the true effect size $\delta$ = 0.5. Effect size estimates stemming from the fixed sample hypothesis test are, as expected, normally distributed around the true effect size ($\delta$ = 0.5). As we can see, the distribution of effect size estimates stemming from the sequential procedures have a somewhat odd shape. This is to be expected [see, for example, @goodman2007]. The distribution of observed effects is more spread out for the sequential procedures because the experiments that stopped early have smaller sample sizes and higher variability in effect size estimates. In addition, we observe left-tailed peaks in the distribution of observed effect sizes. This is a consequence of those experiments that stopped early with a decision to support the null (i.e., False Negative results).

For the group-sequential designs, we can see that the available median-unbiased estimators provide a great improvement over the naive (Cohen's *d*) estimator. For both the Pocock-like and the O'Brien-Fleming-like designs, the bias-adjusted effect size estimate is very close to the true population effect size: *d* = 0.49 compared to $\delta$ = 0.50. For the SBF procedure, we see that the using the mean of the posterior distribution (which shrinks the effect size estimate in earlier terminations) also provides a slight improvement in parameter estimation (by reducing the estimated effect size from *d* = 0.57 to *d* = 0.55).  The bias in the median effect size estimate of the ISP, however, is severe (*d* = 0.66; an exaggeration ratio of 1.33). This biased estimate remains uncorrected due to the absence of a bias-adjusted estimator accompanying the ISP. A we can see, the distribution of effect size estimates stemming from the ISP is bimodal.

@@

In figures S1-S4 in the supplemental files, readers can find that this observation is not merely idiosyncratic to the test chosen (a two-sample *t* test with $\alpha$ = .05 and $\beta = .20$ for a hypothesized population effect size $\delta$ = 0.5). In contrast, across dozens of different test specifications, effect size estimates stemming from the ISP are consistently bimodal and systematically exclude the true population effect size from being observed.

@@

<!-- Add in discussion/limitation section: We do not discuss adaptive designs, which extend GS designs and allow for even more flexibility while controlling error rates.  -->
<!-- List recommendations: for OBF, set unequally spaced looks. For SBF, run simulations to choose an optimal sample size, decision threshold, and prior distribution. -->
<!-- Discuss the power of the individual segments. Practical advice (can lead to guidance on choosing alpha strong; make sure that the alpha strong you set does not exclude the effect size you are interested in. Write reveal.effectsize function): You have to make sure that the individual segments are each powered to at least 50 percent to detect the hypothesized effect size: otherwise, the critical effect size will be higher than the hypothesized effect size, and you will thus systematically discard the effect sizes that you intended to detect! Show that with the example used, the first two independent segments are powered to ~30%. In all but the last segment, the critical effect size (the effect size you need to observe to claim significance) is a factor larger than the actual population effect that you powered your test for. It is thus impossible to get an unbiased estimate out of anything but the last segment.  When you obtain an effect size close to the true effect, the ISP procedure forces you to continue to the last segment, and *throw out that data*. (You can even graph this exaggeration ratio: create a table that shows the exact critical effect size for all possible combinations, and then you can just read off that plot that you're setting yourself up for overestimation). -->
<!-- Discuss conditional bias (bias in effect size estimates conditional on stopping early) and unconditional bias (bias in effect size estimates across all studies). All other procedures have low unconditional bias, when you take the late termination studies into account, because they do cumulative analyses — the late termination studies are able to compensate for the bias in the early stage terminations. However, because the independent segments procedure is independent, each individual segment is biased and this is never accounted or compensated for. Thus, the ISP is unique among sequential procedures in that it not only has strong conditional bias (like most sequential procedures): it also has strong unconditional bias. [In this paper, I focused on two properties: conditional bias (bias in effect size estimates conditional on stopping early) and unconditional bias (bias in effect size estimates across all studies). I show that the independent segments procedure is unique among sequential procedures in that it not only has strong conditional bias (like all sequential procedures); it also has strong unconditional bias.] Emphasize that this is also what we see in Figure 3B: we only reject when d > 0.57. (This is not the case for, e.g., Pocock)   -->
<!-- In the language of decision theory, the ISP is inadmissible: its total squared error risk exceeds that of other hypothesis testing procedures no matter what the true effect size may be.  -->
<!-- Also refer to MSE as reducible error  -->
<!-- Emphasize that there is no bias correction available for the ISP, while there is for the SBF and GS.  -->
<!-- (To make the point that the setup of the simulations is more practical and realistic than previous ones), Show some data on what scientists actually do, e.g., how often they look at their data when they use the Sequential Bayes Factor. Here's some examples on how SBFs are used in practice https://github.com/nicebread/BFDA/blob/master/BFDA_examples.md  -->

@@

```{r, echo = FALSE}
E_n = df %>% 
  group_by(name, d_actual) %>% 
  summarize(E_n = mean(n_cumulative)) %>% 
  rename(Procedure = name)

t3 = E_n %>% mutate(E_n = E_n %>% round()) %>% 
  pivot_wider(names_from = d_actual, names_prefix = "*d* = ", values_from = E_n)

knitr::kable(t3)
```
